Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area" \\ [1ex] \large Supplementary Information

### 2022-02-13 paper/suppl.tex
let suppl.tex use {naturemage}

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
    \caption[Participant-specific surface plots of primary contrasts]
    {Fixed-effects individual-level GLM results ($Z$>3.4; $p$<.05
        cluster-corrected) projected onto reconstructed subject-specific brain
        surfaces.
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-       geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (red) that compares cuts to a setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black: outline of participant-specific PPA ROIs reported by
        \citet{sengupta2016extension} that was spatially smoothed by applying a
        Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
        }
    \label{fig:subjs_ao_av_c1_surf}
\end{figure*}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices-volsurf}
    \caption[Group results across contrasts of movie and audio-description]
    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
    corrected) across all contrasts for both naturalistic stimuli.
    The audio-description's contrasts 1-8 (blue)
    are overlaid over the audio-visual movie's contrasts 1-5 (red;
    see Table~5)
    . %\ref{tab:contrasts}).
    % volume
    a) results as brain slices on top of the MNI152 T1-weighted head template,
    with the acquisition field-of-view for the audio-description study
    highlighted.
    % PPA
    For comparison depicted as a black outline, the union of the
    individual PPA localizations reported by \citet{sengupta2016extension}
    that was spatially smoothed by applying a Gaussian kernel with full
    width at half maximum (FWHM) of \unit[2.0]{mm}.
    % surface map
    b) results projected onto the reconstructed
    surface of the MNI152 T1-weighted brain template.
    After projection, the union of individual PPA localizations was
    spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}
    }
    \label{fig:stability-slices-volsurf}
\end{figure*}

@@

{\small\bibliographystyle{unsrtnat}
\bibliography{references}}

>>>>

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/subjs_ao_av_c1_surf}
    \caption[Participant-specific surface plots of primary contrasts]
    {Fixed-effects individual-level GLM results ($Z$>3.4; $p$<.05
        cluster-corrected) projected onto reconstructed subject-specific brain
        surfaces.
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-       geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (red) that compares cuts to a setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black: outline of participant-specific PPA ROIs reported by
        Sengupta et al.
        \citep{sengupta2016extension} that was spatially smoothed by applying a
        Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
        }
    \label{fig:subjs_ao_av_c1_surf}
\end{figure*}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices-volsurf}
    \caption[Group results across contrasts of movie and audio-description]
    {Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster
    corrected) across all contrasts for both naturalistic stimuli.
    The audio-description's contrasts 1-8 (blue)
    are overlaid over the audio-visual movie's contrasts 1-5 (red;
    see Table~5)
    . %\ref{tab:contrasts}).
    % volume
    a) results as brain slices on top of the MNI152 T1-weighted head template,
    with the acquisition field-of-view for the audio-description study
    highlighted.
    % PPA
    For comparison depicted as a black outline, the union of the
    individual PPA localizations reported by Sengupta et al.
    \citep{sengupta2016extension}
    that was spatially smoothed by applying a Gaussian kernel with full
    width at half maximum (FWHM) of \unit[2.0]{mm}.
    % surface map
    b) results projected onto the reconstructed
    surface of the MNI152 T1-weighted brain template.
    After projection, the union of individual PPA localizations was
    spatially smoothed by a Gaussian kernel with FWHM of \unit[2.0]{mm}
    }
    \label{fig:stability-slices-volsurf}
\end{figure*}

@@

{\small\bibliographystyle{naturemag}
\bibliography{references}}
